%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Resume/CV
% XeLaTeX Template
% Version 1.2 (27/3/2017)

% Original author:
% Claud D. Park (posquit0.bj@gmail.com) with modifications by 
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry

\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-red} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{}{Shan Jiang}
\address{Department of Computing, The Hong Kong Polytechnic University}

\email{cssjiang@comp.polyu.edu.hk}
\homepage{jasison27.github.io}
%\github{jasison27}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}
%\linkedin{linkedin name}
%\reddit{reddit account}
%\xing{xing name}
%\extrainfo{test} % Other text you want to include on this line

\position{Ph.D. Candidate} % Your expertise/fields
%\quote{``Make the change that you want to see in the world."} % A quote or statement

\makecvfooter{\today}{Shan Jiang~~~·~~~Résumé}{\thepage} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed

%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

% Education
\cvsection{Education}
\begin{cventries}
\cventry
{Ph.D. in Computer Science} % Degree
{The Hong Kong Polytechnic University} % Institution
{Hong Kong SAR, China} % Location
{Jul. 2016 - Present} % Date(s)
{ % Description(s)
Under the supervision of Prof. Jiannong Cao (Fellow of IEEE)
}

\cventry
{B.Sc. in Computer Science} % Degree
{Sun Yat-sen University} % Institution
{Guangzhou, China} % Location
{Sep. 2011 - Jul. 2015} % Date(s)
{ % Description(s)
Member of University ACM-ICPC team
}
\end{cventries}

% Experience
\cvsection{Experience}
\begin{cventries}
\cventry
{Research Assistant, under the supervision of Prof. Jiannong Cao} % Job title
{Department of Computing, The Hong Kong Polytechnic University} % Organization
{Hong Kong SAR, China} % Location
{Apr. 2011 - Jun. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
Working on distributed algorithms and programming model for multi-robot systems.
}

\cventry
{Software Engineer} % Job title
{Global Market Group} % Organization
{Guangzhou, China} % Location
{Jul. 2014 - Sep. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
Working on Android app development.
}

\cventry
{Software Engineer} % Job title
{Flamingo Network Inc. Co. Ltd.} % Organization
{Guangzhou, China} % Location
{Jul. 2012 - Sep. 2012} % Date(s)
{ % Description(s) of tasks/responsibilities
Working on mobile game development using cocos2d-x.
}
\end{cventries}

% Publication
\cvsection{Publication}
\begin{cvpublications}
\cvpublication
{Journal}
{Xiulong Liu, Jiannong Cao, Yanni Yang, Shan Jiang, ``CPS-Based Smart Warehouse for Industry 4.0: A Survey of the Underlying Technologies'', accepted MDPI Computers} 

\cvpublication
{Conference}
{Jia Wang, Jiannong Cao, Shan Jiang, ``Fault-Tolerant Pattern Formation by Multiple Robots: A Learning Approach'', {\em SRDS} 2017: 268-269 (PhD Forum)}

\cvpublication
{Conference}
{Shan Jiang, Jiannong Cao, Jia Wang, Milos Stojmenovic, Julien Bourgeois, ``Uniform Circle Formation by Asynchronous Robots: A Fully-Distributed Approach'', {\em ICCCN} 2017: 1-9}

\cvpublication
{Book Chapter}
{Yuvraj Sahni, Jiannong Cao, Shan Jiang, ``Middleware for Multi-Robot System'', a chapter to appear in ``{\em The Philosophy of Mission-Oriented Wireless Sensor Networks}''(Springer), Habib M. Ammari (Ed.). 2017.}

\cvpublication
{Conference}
{Shan Jiang, Jiannong Cao, Yan Liu, Jinlin Chen, Xuefeng Liu, ``Programming Large-Scale Multi-Robot System with Timing Constraints'', {\em ICCCN} 2016: 1-9}

\cvpublication
{Conference}
{Shan Jiang, Junbin Liang, Jiannong Cao, Rui Liu, ``An ensemble-level programming model with real-time support for multi-robot systems'', {\em PerCom Workshops} 2016: 1-3 (Demo)}
\end{cvpublications}

\cvsection{Project}
\begin{cventries}
\cventry
{Leader} % Role
{AI3 - A Layered-Federation Information Sharing Architecture} % Project Name
{HK PolyU} % Location
{Sep. 2017 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Proposed and developed TSAR, a fully-distributed Trustless data ShARing platform. It employs Blockchain as the underlying technology.}
\item {Proposed BlocHIE, a BLOCkchain-based platform for Healthcare Information Exchange.}
\end{cvitems}
}

\cventry
{Leader} % Role
{Declarative Programming and Runtime Support for Distributed Coordination of Multirobot Systems} % Project Name
{HK PolyU} % Location
{Jan. 2017 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Improve the multi-robot test-bed concerning hardware. A new demo ``multi-robot pattern formation'' is developed.}
\item {Proposed a fully-distributed approach for multi-robot uniform circle formation problem.}
\item {Investigated the possibility to employ learning approaches in multi-robot systems.}
\end{cvitems}
}

\cventry
{Core Member} % Role
{Coordination and Computation in Distributed Intelligent MEMS} % Project Name
{HK PolyU} % Location
{Apr. 2015 - Aug. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Surveyed existing middleware for multi-robot systems.}
\item {Proposed an ensemble-level programming model supporting time-constraint mechanism.}
\item {Developed a test-bed and a simulation environment for multi-robot systems. The simulator is extended from VisibleSim with supports of action and wireless communication. On the test-bed, a demo that ``multiple robots pass through a narrow corridor'' is developed.}
\item {Wrote the project completion report.}
\end{cvitems}
}
\end{cventries}

% Honors & Awards
\cvsection{Honors \& Awards}
\begin{cvhonors}
\cvhonor
{Second Runner-up (3/33)} % Award
{ACM-HK Programming Contest 2017} % Event
{Hong Kong, China} % Location
{Jun. 2017} % Date(s)

\cvhonor
{Silver Medal (32/182)} % Award
{Beijing Regional Contest, The 39th ACM-Asia Programming Contest} % Event
{Beijing, China} % Location
{Nov. 2014} % Date(s)

\cvhonor
{The Fourth Place (4/147)} % Award
{ACM-Guangdong Provincial Programming Contest 2014} % Event
{Guangzhou, China} % Location
{May. 2014} % Date(s)

\cvhonor
{Outstanding Student with Second-class Scholarship} % Award
{Sun Yat-sen University} % Event
{Guangzhou, China} % Location
{Nov. 2014} % Date(s)

\cvhonor
{Outstanding Student with Third-class Scholarship} % Award
{Sun Yat-sen University} % Event
{Guangzhou, China} % Location
{Nov. 2012} % Date(s)
\end{cvhonors}

% Service
\cvsection{Service}
\begin{cvhonors}
\cvhonor
{Assistant Coach} % Award
{HK PolyU ACM-ICPC Team} % Event
{HK PolyU} % Location
{S2018} % Date(s)

\cvhonor
{Teaching Assistant} % Award
{Distributed Computing (COMP5325)} % Event
{HK PolyU} % Location
{F2017} % Date(s)

\cvhonor
{Teaching Assistant} % Award
{Programming Fundamentals (COMP1011)} % Event
{HK PolyU} % Location
{S2017} % Date(s)

\cvhonor
{Teaching Assistant} % Award
{Computer Communications Networks (COMP312)} % Event
{HK PolyU} % Location
{F2016} % Date(s)

\cvhonor
{Teaching Assistant} % Award
{Algorithm Design and Analysis} % Event
{SYSU} % Location
{F2014} % Date(s)
\end{cvhonors}

\end{document}
